
\documentclass[margin,line,a4paper]{resume}

\usepackage[latin1]{inputenc} %utf8
\usepackage[english,danish]{babel}
\usepackage[T1]{fontenc}
\usepackage{graphicx,wrapfig}
\usepackage{url}
\usepackage[colorlinks=true, a4paper=true, pdfstartview=FitV,
linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}
\pdfcompresslevel=9

% \setlength{\voffset}{-0.75in}
% \setlength{\headsep}{5pt}

\begin{document}
{\sc \Huge Richard Protasov}
\begin{resume}
    \vspace{0.5cm}

    \section{\mysidestyle Personal\\Information}%\vspace{2mm}
    tel: +1 561 577 4936 \\
    \href{mailto:richard.shlyakhov15@ncf.edu}{richard.shlyakhov15@ncf.edu} \\
    \href{http://protasov.me}{protasov.me}\\
    \href{https://github.com/rprotasov}{github.com/rprotasov}
    
     Richard is a naturally curious person with an excellent attitude toward learning; with an eagerness to delve further, often they are asking questions about concerns regarding readings. An interest of theirs is the use of topics in computer science and urban studies to aid planners and designers. At the moment they are exploring the use of image forecasting through understanding the dependencies between human behavior and an urban streetscape.
    
    \section{\mysidestyle Education}
        \textit{August 2015 - Present}\\
        \textbf{New College of Florida, Bachelors in Computer Science}
        
    \section{\mysidestyle Courses}
        Introduction to Algorithms, Computer Networks, Programming in Python, Object Oriented Programming, Object Oriented Design, Discrete Mathematics, Calculus I and II, Linear Algebra, Advanced Linear Algebra, Dealing with Data, Introduction to Data Mining, Computer Systems, Cryptography and Security, Computer Vision
    
    \section{\mysidestyle Experience}
        \textit{May 2016 - Present}\\
        \textbf{Focus School Software} - \textbf{Software Engineer Intern}\\
        Develop a creative landing page detailing summary statistics for employees in the redevelopment of the human resources package. Maintain legacy software for report cards, human resources, student applications, and miscellaneous modules in the finance package.  Working with PHP, SQL, Javascript, Laravel, Angular, SVN, and various in-house libraries. 
            
        \textit{August 2016 - December 2016}\\
        \textbf{New College of Florida} - \textbf{Teaching Assistant}\\
        Computer Architecture -  assist students with theoretical and technical topics through weekly office hours, weekly labs, and working with the class\textquotesingle professor to write tests along with provide feedback on the material.
    
    \section{\mysidestyle Projects}
        \textbf{Harald}\\
        Development of an open source library in Rust. Provides an implementation of the Bluetooth Low Energy interface.
        
        \textbf{Edsger}\\
        A web application allowing users to                              calculate an efficient route given
        multiple locations and criteria. Developed
        using the Laravel framework, MySQL, and the Google Map APIs this project merges the understanding of relational database design and applied graph theory.
        
    \section{\mysidestyle Graduate\\Courses}
        Optimization and Machine Learning, Distributed Computing

\end{resume}
\end{document}
